### 2023-02-13 chapters/acknowledgements.tex
ack todo

With utmost humility, I would like to take this opportunity to express my sincere gratitude to everyone who has supported me throughout my PhD journey.

@@

I have also been blessed to work with exceptional collaborators, including Debabrota Basu, Dmitry Malioutov, Daniel Neider, Naheed Anjum Araafat, Jonathan Scarlet, and Lorenzo. They have generously shared their knowledge and experience with me and have helped me broaden my perspectives. I have come to understand that finding a meaningful research problem is a crucial step and I am grateful to have had the opportunity to collaborate and brainstorm with such insightful colleagues and friends.

>>>>

\todo{Incomplete}With utmost humility, I would like to take this opportunity to express my sincere gratitude to everyone who has supported me throughout my PhD journey.

@@

I have also been blessed to work with exceptional collaborators, including Debabrota Basu, Dmitry Malioutov, Daniel Neider, Naheed Anjum Arafat, Jonathan Scarlet, and Lorenzo. They have generously shared their knowledge and experience with me and have helped me broaden my perspectives. I have come to understand that finding a meaningful research problem is a crucial step and I am grateful to have had the opportunity to collaborate and brainstorm with such insightful colleagues and friends.
